Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
Add a note

This also means that typical usage examples cannot be found from test code.
We agree that type signatures are good abstract document but
there are many functions whose behaviors cannot be guessed from
their names and type signatures.

>>>>

This also means that typical usage examples cannot be found from test code.

We agree that type signatures are good abstract document

\begin{quote}
    \emph{Should we quote "Theorems for free!" by P. Wadler here?}
\end{quote}

but there are many
functions whose behaviors cannot be guessed from their names and type
signatures.
